% Chapter Template

\chapter{Sustainability Report} % Main chapter title

\label{Chapter6} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

% \section{Environmental}
% \section{Economic}
% \section{Social}
% \begin{note}
%   \subsection{Impacto Personal}
% \end{note}
%   \begin{note}
%     \subsection{Impacto Social}
%   \end{note}
%   \begin{note}
%     \subsection{Riesgos Sociales}
%   \end{note}


  \section{Project description}

  \textbf{Using Random Fourier Features with Random Forest} is a project that
  that has the objective of studying the advantages of using feature maps that
  approximate a Kernel Function together with other Machine Learning techniques.

  Through the usage of Random Fourier Features and the \Nys\ method, we want to see
  if it is possible to increase the accuracy of three Machine Learning algorithms:
  Logistic Regression, Support Vector Machines and Random Forest.

  \section{Sustainability matrix}

  \begin{table}[H]
\begin{tabular}{|l|l|l|l|}
\hline
                       & \textbf{Deployment} & \textbf{Lifespan} & \textbf{Risks} \\ \hline
\textbf{Environmental} & 10                   & 10                 & 10              \\ \hline
\textbf{Economic}      & 10                   & 7                 & 6              \\ \hline
\textbf{Social}        & 10                   & 10                 & 10              \\ \hline
\end{tabular}
\end{table}


  \section{Project deployment}
    \subsection{Environmental}
      \subsubsection*{First Milestone}

    The estimates for the needed resources during the deployment of the project
    consider a single employee as an expert in Machine Learning and Data Science.
    The technological requirements of the project are a laptop, the energy to
    keep it working and a connection to the Internet. In addition to that, it will
    be needed a suitable place to develop the study.

    The laptop doesn't need to have a very high specification, and hence it was
    preferred to reuse and old laptop than to buy a new one. For this reason, there
    is no power consumption nor negative effect in the environment for the deployment
    of this project.


    \subsubsection*{Last Milestone}

    There was no power consumption or negative effect in the environment for the deployment
    of this project.

    \subsection{Economic}
      \subsubsection*{First Milestone}

      All the software used for this project will be free, so there are no costs
      regarding that.

      Although there is no need to buy a new laptop for this project, an existing
      one needs to be moved away from other stuff, and that has a cost. The
      estimated cost of that is of 400 €.

      \subsubsection*{Last Milestone}

      The economic estimate in the first milestone was correct: there have not
      been any additional economic costs in the project.

    \subsection{Social}
      \subsubsection*{First Milestone}

      There are no social effects during the deployment of this project.

      \subsubsection*{Last Milestone}

      Effectively, there where no social effects during the deployment
      of this project.

  \section{Lifespan}
    \subsection{Environmental}
      \subsubsection*{First Milestone}

      The power consumption of the laptop is 10 W, and the power needed to maintain the
      office is approximately 0.24 kW, so the total consumption of the project is
      0.25 kW.

      Since the project is expected to last 240 hours of work, the total consumption of
      the project 0.25 kW $\times$ 240 h = 60 kWh


      \subsubsection*{Last Milestone}

      There where many changes in the planning and the scope of the project,
      and the amount of hours of work turned out being 750. So the total consumption
      of the project has been 0.25 kW $\times$ 750 h = 187.5 kWh.

    \subsection{Economic}
      \subsubsection*{First Milestone}

      The economic costs of this project during the lifespan will be the
      wage of the only one employee, which is an expert in Machine Learning
      and Data Science, and the costs of the power consumption.

      Since the project is expected to require 240 hours of work, and assuming
      a wage of 30 € / hour, the total cost of the wage is
      240 hours $\times$ 30 € / hours = 7200 €

      The total power consumption of the project is 187.5 kWh, and the
      approximate cost of a kWh is 0.12 €. So the total cost from power
      consumption is 60 kWh $\times$ 0.12 €/kWh = 7.2 €

      So, the total costs of the project will be
      7200 € + 7.2 € = 7207.2 €

      \subsubsection*{Last Milestone}

      In the end the total hours of work were 750, not 240, so the
      cost was 750 h $\times$ 30 € / h + 750 h $\times$ 0.25 kW $\times$ 0.12
      € / kWh = 22500 € + 22.5 € = 22522.5 €
    \subsection{Social}
      \subsubsection*{First Milestone}

      The only social effects that this project will have during the lifespan
      of the project is that the Machine Learning expert that is employed
      will have a occupation for 240 hours and will not be handy for other
      works.

      \subsubsection*{Last Milestone}

      Since the project took more time than expected, the worker was employed
      for more time.

    \section{Risks}
      \subsection{Environmental}
        There are no environmental risks for this project.

      \subsection{Economic}

      The economic risk for this project is that after investing many
      hours in this project, the conclusions achieved with the study
      are useless. In any case, this will avoid that other researchers
      invest time and resources to study The same thing.

      \subsection{Social}

      Since this project is about investigation, there are no social risks
      related to it, but with what people do with that knowledge.
      Nevertheless, increasing the accuracy of Machine Learning Models
      is not expected to have a negative impact on society.
